I am a title (RO SLAM Methods/Implementation Survey)

### 2018-01-14 Paper.tex
Add all the paper references to a .bib
All the papers we found should now be able to be referenced,

Just gotta go to the references.bib file and look for the key to the reference.

The references were mendaly exported

%just a test references section

%use mendaly 
\begin{filecontents*}{references.bib}
	@article{Khoe:1994:CML:2288694.2294265,
		author = {Khoe, G. -D.},
		title = {Coherent multicarrier lightwave technology for flexible capacity networks},
		journal = {Comm. Mag.},
		issue_date = {March 1994},
		volume = {32},
		number = {3},
		month = mar,
		year = {1994},
		issn = {0163-6804},
		pages = {22--33},
		numpages = {12},
		url = {http://dx.doi.org/10.1109/35.267438},
		doi = {10.1109/35.267438},
		acmid = {2294265},
		publisher = {IEEE Press},
		address = {Piscataway, NJ, USA},
	}
\end{filecontents*}

@@

@@

	\bibliographystyle{ieeetran}
	\bibliography{references}

>>>>

@@

%test citation
\cite{Blanco2008}

@@

	\bibliographystyle{IEEEtran}
	\bibliography{references}
